---
title: "Adolescents flexibly adapt action selection based on controllability inferences"
author: "Noam Goldway and Hillary Raab"
date: "2023-10-04"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries

```{r libraries}
library(R.matlab)
library(tidyverse)
library(dplyr)
library(gridExtra)
library(pander)
library(psych)
library(afex)
library(cowplot)
library(nlme)
library(emmeans)
library(rempsyc)
library(modelbased)
library(see)
library(report)
library(grid)
library(ggplot2)
library(lme4)
library(segmented)
library(segmented)


```
## Define working directory
```{r wd}
#Your main WD goes here: 
WD<-''
```


## Data Import and Cleaning

```{r data_cleaning}

path<-paste0(WD,'data/task_data/')
studyIDAll_chr <-  list.files(path)
studyIDAll_chr <- studyIDAll_chr[!grepl('Excluded', studyIDAll_chr)]
studyIDAll <- str_remove_all(studyIDAll_chr,"ConPit")
studyIDAll <- as.numeric(studyIDAll)
studyIDAll_chr <- paste(studyIDAll,"ConPit",sep="")
allPIT <- data.frame()

for(subj in 1:length(studyIDAll_chr)){
  data <- readMat(paste0(path,studyIDAll_chr[subj],"/",studyIDAll[subj],"_TaskDataLearning_Session1.mat"))
  data <- as.data.frame(data)
  data <- cbind(subjID = studyIDAll[subj], data) 
  allPIT <- rbind(allPIT,data)
}

colnames(allPIT) <- c("subjID","trialNum","trialType","timeCue","response1Cue","response2Cue","time2target","timeTarget","keyResp","keyTime","RT","Response","corrResp","foil","targetDisplayTime","timeOutcome","ITI","Won","Condition")

allPIT$subjID <- as.factor(allPIT$subjID)
allPIT$Condition <- as.factor(allPIT$Condition)
allPIT$trialType <- as.factor(allPIT$trialType)
levels(allPIT$trialType) <- c("GW","GAL","NGW","NGAL") #rename

### LOAD AGE DATA
age.csv<-paste0(WD,'data/age_cov_n90.csv')
age <- read.csv(age.csv, header = TRUE, stringsAsFactors = FALSE)
```


```{r data_preprocessing}

age <- age %>%
  mutate(subjID = str_remove_all(subjID, "ConPit"))
age$subjID <- as.factor(age$subjID)
age$gender <- as.factor(age$gender)
age$z_age<-scale(age$age,center=TRUE,scale=TRUE) #age as continuous variable, mean centered and scaled
age$z_ageSq<-age[,"z_age"]^2

age$Age.Group <- factor(age$Age.Group, levels=c('Child','Teen','Adult')) #order by age
levels(age$Age.Group) <- c("Children","Adolescents","Adults") #rename

allPIT <- merge(allPIT,age,by="subjID")
allPIT$Condition <- factor(allPIT$Condition, levels=c('8020','5050'))
levels(allPIT$Condition) <- c("Controllable","Uncontrollable") #rename

### REMOVE TRIALS RESPONDED EARLY
allPIT <- allPIT[allPIT$Response!=5,]
allPIT <- allPIT[allPIT$Response!=3,]

#plot colors
color1 = "#3A1142"
color2 = "#35877F"

```


```{r manipulation_and_preparation }

# Calculate the total tickets won per subject 
PavBias_overall <- allPIT %>% 
  group_by(subjID, age, z_age, z_ageSq, Age.Group) %>% 
  summarize(totalTickets = sum(Won, na.rm = TRUE))

# Calculate tickets won per condition 
PavBias_byCondition <- allPIT %>% 
  group_by(subjID, Condition, age, z_age, z_ageSq, Age.Group) %>% 
  summarize(tickets = sum(Won, na.rm = TRUE))

# Calculate the difference in tickets won between different conditions
PavBias_byCondition <- PavBias_byCondition %>% 
  group_by(subjID, age, z_age, z_ageSq, Age.Group) %>% 
  mutate(diffTickets = lag(tickets) - tickets)

```

##  Plot Tickets Won per Condition 

```{r visualization}

# Create a scatter plot with smoothed lines per condition
ticketsWon_condition_plot <- ggplot(PavBias_byCondition, aes(x = z_age, y = tickets, color = Condition)) +
  geom_point(size = 2) +
  geom_smooth(method = "glm", formula = y ~ poly(x, 2)) +
  geom_hline(yintercept = 0, size = 2, linetype = "dashed", color = "black") +
  labs(x = "Age", y = "Tickets won") +
  theme_classic(base_size = 12) +
  scale_color_manual(values = c(color1, color2))

# Display the created plot
plot(ticketsWon_condition_plot)

```

##  Model Comparisons - Tickets Won

```{r model_comparisons }


TicketsConAge.m <- lm(tickets ~ Condition * z_age, data = PavBias_byCondition)
TicketsConAgeSq.m <- lm(tickets ~ Condition * (z_age + z_ageSq), data = PavBias_byCondition)

# Compare models 
anova(TicketsConAge.m, TicketsConAgeSq.m)
AIC(TicketsConAge.m, TicketsConAgeSq.m)
summary(TicketsConAgeSq.m)


```

## Piecewise Linear Regression Tickets Won

```{r piecewise_regression }

# Select data and convert to numeric
data_for_change <- subset(PavBias_byCondition, Condition == "Controllable", 
                          select = c(tickets, z_age))
data_for_change$z_age <- as.numeric(as.character(data_for_change$z_age))
data_for_change$tickets <- as.numeric(as.character(data_for_change$tickets))

# Perform piecewise linear regression
model_pw <- segmented(lm(tickets ~ z_age, data = data_for_change))

# Extract and output model details
summary(model_pw)  
model_pw$psi  # Estimated breakpoint in z_age=0.031 which correspond to 16.5 years 

# Derive and display t-values and p-values
slope_t <- slope(model_pw)
t_value_pre <- slope_t$z_age[5]
t_value_post <- slope_t$z_age[6]
n <- nrow(data_for_change)
p <- 2 + length(model_pw$psi)  # Parameters: Intercept, slope(s), and breakpoints
df <- n - p  # Degrees of freedom
t_values <- c(t_value_pre, t_value_post)
p_values <- 2 * (1 - pt(abs(t_values), df))


```

##  Model Free Pavlovian Bias 

```{r pavlovian_bias }
# #add presses on go to win + presses on no go to win then divide that by all presses; reward based invigoration
calculate_RewInv <- function(x){((sum(x$trialType=='GW' & x$Response=='1')) + (sum(x$trialType=='NGW' & x$Response=='1'))) / (sum(x$Response=='1'))} 
# 
# #add no presses on go to avoid + no presses on no go to avoid then divide that by all no presses; punishment-based suppression
calculate_PunSupp <- function(x){((sum(x$trialType=='GAL' & x$Response=='0')) + (sum(x$trialType=='NGAL' & x$Response=='0'))) / (sum(x$Response=='0'))} 


#separate into controllable and uncontrollable trials
All_pit_8020 <- allPIT[allPIT$Condition %in% "Controllable",]
All_pit_5050 <- allPIT[allPIT$Condition %in% "Uncontrollable",]

RewInv <- by(data = All_pit_8020, INDICES = All_pit_8020$subjID, FUN = calculate_RewInv)
PavBias_overall$con_rewInv <- RewInv

PunSupp <- by(data = All_pit_8020, INDICES = All_pit_8020$subjID, FUN = calculate_PunSupp)
PavBias_overall$con_punSupp <- PunSupp

PavBias_overall$con_PavPerBias <- (RewInv + PunSupp)/2
remove(RewInv,PunSupp)

RewInv <- by(data = All_pit_5050, INDICES = All_pit_5050$subjID, FUN = calculate_RewInv)
PavBias_overall$uncon_rewInv <- RewInv

PunSupp <- by(data = All_pit_5050, INDICES = All_pit_5050$subjID, FUN = calculate_PunSupp)
PavBias_overall$uncon_punSupp <- PunSupp

PavBias_overall$uncon_PavPerBias <- (RewInv + PunSupp)/2
remove(RewInv,PunSupp)

pavbiascombined <- gather(PavBias_overall, condition, PavBiasScore, con_PavPerBias,uncon_PavPerBias, factor_key=TRUE)
pavbiascombined<- pavbiascombined%>%dplyr::select(c('subjID','age', 'z_age', 'z_ageSq', 'Age.Group', 'condition','PavBiasScore'))
pavbiascombined$subjID <- as.factor(pavbiascombined$subjID)
pavbiascombined$condition <- as.factor(pavbiascombined$condition)
levels(pavbiascombined$condition) <- c("Con","Uncon") #rename
```

##   Mixed-Effects Model Analyse Pavlovian Bias 

```{r  model_comparisons_pavlovian_bias }

PavBias.age.m <- mixed(PavBiasScore ~ condition*(z_age) + (1 | subjID), data = pavbiascombined, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))
nice(PavBias.age.m)

PavBias.ageSq.m <- mixed(PavBiasScore ~ condition*(z_age+z_ageSq) + (1 | subjID), data = pavbiascombined, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))
anova(PavBias.age.m,PavBias.ageSq.m) #adttion of age^2 is not justified 


PavBias.age.group.m <- mixed(PavBiasScore ~ condition*Age.Group + (1 | subjID), data = pavbiascombined, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))
age_con <- emmeans(PavBias.age.group.m, pairwise ~ condition | Age.Group)
age_con #print post hoc results 

# Get the estimated marginal means for the interaction
emm_int <- emmeans(PavBias.age.group.m, ~ condition * Age.Group)

# Pairwise comparisons of the interaction effect
con_delta <- contrast(emm_int, interaction = "pairwise")
con_delta # Print the results
```


###  Visualization: Pavlovian  Bias 

```{r visualization_pavlovian_bias }

PavBiasByAgeBin <- pavbiascombined %>%
  group_by(condition, Age.Group) %>%
  summarise(N = n(), meanBias = mean(PavBiasScore, na.rm = TRUE), sdBias = sd(PavBiasScore, na.rm = TRUE), seBias = sdBias / sqrt(N))

# Plot figure 3
condition_PavBias <- ggplot(PavBiasByAgeBin, aes(x = condition, y=PavBiasScore)) +
  geom_point(data= pavbiascombined, aes(x=condition,y=PavBiasScore,group=subjID,color=Age.Group)) +
  geom_line(data= pavbiascombined, aes(group=subjID,color=Age.Group),size =1,alpha=.5) +
  geom_line(data = PavBiasByAgeBin, stat = "identity", aes(group=Age.Group,x=condition,y=meanBias),size=2,color="Black") +
  geom_errorbar(data = PavBiasByAgeBin, aes(x=condition, y=meanBias, ymin = meanBias - seBias, ymax = meanBias + seBias), width=0.2) +
  facet_wrap(~Age.Group)  + 
  expand_limits(y=1.05)+   scale_y_continuous(breaks=c(0.25,0.5,0.75,1))+
  theme_classic(base_size=20)+
  geom_hline(yintercept=.5, linetype="dashed", color = "black") +
  labs(y="Pavlovian performance bias", x= "Condition") + scale_x_discrete(limits=c("Con", "Uncon")) + #label x axis and y-axis
  theme(legend.position = "None", ) + #change theme
  scale_color_manual(values = c("steelblue2", "steelblue3","steelblue4"))
plot(condition_PavBias)

```

## Dynamic Pavlovian Weight (w) 

### Data Import and Merging

```{r dynamic_w_data}
w.csv<-paste0(WD,'data/w_trial_by_trial.csv')
w_trialbytrial <- read.csv(w.csv, header = FALSE, stringsAsFactors = TRUE)
colnames(w_trialbytrial) <- c("subjID", "trial_num", "action", "trial_type", "condition", "w")
w_trialbytrial$subjID <- as.factor(w_trialbytrial$subjID)
w_trialbytrial$condition <- factor(w_trialbytrial$condition, levels = c('8020', '5050'))
levels(w_trialbytrial$condition) <- c("Con", "Uncon")
w_trialbytrial <- merge(w_trialbytrial, age[, c("subjID", "age", "Age.Group", "z_age", "z_ageSq")], by = "subjID")

firstTrial <- allPIT %>%
  group_by(subjID, Condition) %>%
  dplyr::summarize(minTrialNum = min(trialNum)) %>%
  filter(minTrialNum <= 180) %>%
  rename(Order = Condition) %>%
  dplyr:: select(-minTrialNum)

w_trialbytrial <- merge(w_trialbytrial, firstTrial, by = "subjID")
w_trialbytrial$Order <- ifelse(w_trialbytrial$Order == 'Controllable', 'Controllable first',
                               ifelse(w_trialbytrial$Order == 'Uncontrollable', 'Uncontrollable first', NA))

w_trialbytrial <- w_trialbytrial %>%
  mutate(z_trial_num = scale(trial_num),
         trial_num_per_con = ifelse(trial_num > 180, trial_num - 180, trial_num),
         z_trial_num_per_con = scale(trial_num_per_con),
         block = ifelse(trial_num < 180, '1st Block', '2nd Block'),
         block = as.factor(block))

order_per_subj <- w_trialbytrial %>%
  distinct(subjID, Order)
```

### Pavlovian Weight (w) by Age Group and Trial Condition Order

```{r plot_w, fig.cap="Line plot of the mean Pavlovian weight (w) by age group and trial condition order, with error bars indicating standard error of the mean."}
w_trialbytrial_order_per_agegroup <- w_trialbytrial %>%
  group_by(Age.Group, trial_num, condition, Order) %>%
  dplyr::summarise(N = n(), mean_w = mean(w, na.rm = TRUE), sdw = sd(w, na.rm = TRUE), sew = sdw / sqrt(N))


w_byagetrialcondition_order <- ggplot(w_trialbytrial_order_per_agegroup, aes(x = trial_num, y = mean_w, color = condition)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_w - sew, ymax = mean_w + sew), alpha = 0.1) +
  facet_wrap(~Age.Group) +
  geom_vline(xintercept = 180, size = 1.5, linetype = "dashed", color = "black") +
  theme_classic(base_size = 20) +
  theme(axis.title.x = element_blank()) +
  ylab('Pavlovian weight (w)') +
  labs(color = "Condition") +
  scale_color_manual(values = c(color1, color2)) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  scale_x_continuous(breaks = c(90, 270), labels = c("Block 1", "Block 2"))

plot(w_byagetrialcondition_order)
```

### Mixed-Effects Model Analyses W

```{r w_model}



w.m <- mixed(w ~ Age.Group * z_trial_num_per_con * Order * condition + (z_trial_num_per_con * condition + 1 | subjID), data = w_trialbytrial, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))
nice(w.m)



# Post hoc test function
run_post_hoc <- function(model, spec, contrasts_at, adjust_method = "none", limit = 41474){
  effects <- emmeans(model, spec, adjust = adjust_method, pbkrtest.limit = limit)
  print(contrast(effects, method = "pairwise", at = contrasts_at))
}

# Run post hoc tests
run_post_hoc(w.m, ~ condition, list(block = c("Controllable", "Uncontrollable")))
run_post_hoc(w.m, ~ Order, list(block = c("Con first", "Uncon first")))
run_post_hoc(w.m, pairwise ~ condition | Age.Group, list(block = c("Con first", "Uncon first")))
run_post_hoc(w.m, ~ condition | Order, list(block = c("Con first", "Uncon first")))
```


#####supplemental data#### 

## Age histogram

```{r age_histogram}

##age histogram
pander(count(age, Age.Group, gender))

pander(describeBy(age))

ageHistogram <- ggplot(age, aes(x = floor(age), fill = gender)) + geom_bar() +
  ylab("Participant Count") + xlab("Age") + guides(fill=guide_legend(title="Gender")) +
  geom_vline(xintercept=12.5, linetype="dashed", color = "black") + 
  geom_vline(xintercept=17.5, linetype="dashed", color = "black") + 
  theme_classic(base_size=14) 
plot(ageHistogram)

```

### Computational model comparison
```{r model_comparison}

se <- function(x) {
  sd(x, na.rm = TRUE) / sqrt(length(x))
}
BIC.csv<-paste0(WD,'computational_modeling_code/BIC.csv')
BIC_models <- read_csv(BIC.csv)

mean_bic <- BIC_models %>%
  pivot_longer(cols = -subjID, names_to = "model", values_to = "bic") %>%
  dplyr::group_by(model) %>%
  dplyr::summarise(mean_bic = mean(bic),  N = n()) %>%
  mutate(model_name = fct_reorder(model, desc(mean_bic)))


ggplot(mean_bic, aes(x = model_name, y = mean_bic, fill = model_name)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  geom_text(aes(label = round(mean_bic, 1)), vjust = -0.6, color = "black", size = 4) +
  scale_fill_brewer(palette = "Blues") +
  coord_cartesian(ylim = c(350, 390)) +
  ylab("Mean BIC") +
  theme_classic(base_size = 12) +
  theme(
    legend.position = "right",
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
  ) +
  labs(fill = "Model name")
```


### Posterior predictive checks 
```{r PPC }
sim_data_path<-paste0(WD,'computational_modeling_code/pcc/')

sim_data_file_list <- list.files(path = sim_data_path, pattern = "\\.csv$", full.names = TRUE)

sim_data <- data.frame()  # Create an empty data frame

for (i in 1:length(sim_data_file_list)) {
  temp_data <- read.csv(sim_data_file_list[i])
  temp_data <- as.data.frame(temp_data)
  subji <- gsub("Sim_subji_(\\d+)\\.csv", "\\1", basename(sim_data_file_list[i]))  # Extract subji from file name
  temp_data$sim_subji <- subji  # Add subji as a variable
  sim_data <- rbind(sim_data, temp_data)  # Append temp_data to sim_data
}

sim_data <- sim_data %>%
 dplyr:: rename(subjID = subj_i)

# stim:
# 1: GotoWin
# 2: GotoAvoid
# 3: NoGotoWin
# 4: NoGotoAvoid
sim_data$trialType <- case_when(
  sim_data$state == 1 ~ "GW",
  sim_data$state == 2 ~ "GAL",
  sim_data$state == 3 ~ "NGW",
  sim_data$state == 4 ~ "NGAL",
  TRUE ~ NA_character_
)

###condition
sim_data$condition <- case_when(
  sim_data$block == 5050 ~ "Uncon",
  sim_data$block == 8020 ~ "Con",
  TRUE ~ NA_character_
)

sim_data <- merge(sim_data, age, by = "subjID")


###action

sim_data<-  sim_data %>%
  mutate(go = case_when(
    action == 1 ~ 0,
    action == 2 ~ 1,
  ))


sim_action_per_sub_trialType_condition <- sim_data %>% dplyr::group_by(condition,trialType,subjID,Age.Group) %>% dplyr::summarize(meanGo = mean(go, na.rm = TRUE),N = n(), sdAcc = sd(go, na.rm = TRUE),seAcc = sdAcc/(sqrt(N)))

sim_action_trialType_condition <- sim_action_per_sub_trialType_condition %>% dplyr::group_by(condition, trialType,Age.Group) %>% dplyr::summarise(N = n()/10, meanGo_age = mean(meanGo, na.rm = TRUE), sdAction = sd(meanGo, na.rm = TRUE), seAction= sdAction/(sqrt(N)))

sim_action_trialType_condition<-sim_action_trialType_condition %>% dplyr::rename(Condition=condition)

sim_action_trialType_condition<-  sim_action_trialType_condition %>%
  mutate(Condition = case_when(
    Condition == "Con" ~ "Controllable",
    Condition == "Uncon" ~ "Uncontrollable"
  ))


Realaction_per_trialType_condition <- allPIT %>% dplyr::group_by(Condition,trialType,Age.Group) %>% dplyr::summarize(meanGo = mean(Response, na.rm = TRUE),N = n()/45, sdAcc = sd(Response, na.rm = TRUE),seAcc = sdAcc/(sqrt(N)))

condition_go_responses <- ggplot(Realaction_per_trialType_condition, aes(x = trialType, y = meanGo)) + 
  geom_bar(aes(fill = trialType), stat = "identity", color = "Black") +
  scale_fill_manual(values = c("#9084A5", "#BBB3C9", "#BBB3C9", "#9084A5")) + 
  facet_wrap(~Condition + Age.Group) +
  geom_point(data = sim_action_trialType_condition, aes(x = trialType, y = meanGo_age),
             size = 4, color = "yellow", alpha = 0.7) +
  geom_errorbar(data = sim_action_trialType_condition, aes(x = trialType, y = meanGo_age, ymin = meanGo_age - seAction, ymax = meanGo_age + seAction),
                width = 0.2, color = "yellow") +
  geom_errorbar(data = Realaction_per_trialType_condition, aes(x = trialType, y = meanGo, ymin = meanGo - seAcc, ymax = meanGo + seAcc),
                width = 0.3) +
  theme_classic() + 
  theme(strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 20), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.title = element_text(size = 20), 
        legend.text = element_text(size = 20), 
        legend.title = element_text(size = 20),
        legend.position = "none") +
  labs(x = "Trial Type", y = "Go Response")

plot(condition_go_responses)
```


###Correlation between parameters and age 
```{r parameters_age }


# File paths

param.csv<-paste0(WD,'computational_modeling_code/w2_param_estim.csv')
param_df <- read.csv(param.csv, header = FALSE) %>%
  # Assign column names to the dataframe
  `colnames<-`(c("subjID", "invTemp", "reward", "alpha", "w2")) %>%
  # Exclude the first row
  slice(-1)

# Merge parameter dataframe with age data
param_df_age <- merge(param_df, age, by = "subjID")

# Convert parameter columns to numeric
param_df_age <- param_df_age %>%
  mutate(across(c("invTemp", "reward", "alpha", "w2"), as.numeric))

# Merge PavBias_overall with parameter-age dataframe 
PavBias_overall <- merge(PavBias_overall, param_df_age, by = "subjID")

PavBias_overall <- PavBias_overall %>% 
  dplyr::select(-matches("\\.y"))
colnames(PavBias_overall) <- gsub("\\.x", "", colnames(PavBias_overall))

# Define a function to extract correlation results
get_cor_results <- function(data, x, y) {
  result <- data %>%
    summarise(
      correlation = cor.test(get(x), get(y))$estimate,
      p_value = cor.test(get(x), get(y))$p.value
    )
  return(result)
}

# Function to generate plot for each parameter
generate_plot <- function(data, x_var, y_var, title) {
  p <- ggplot(data, aes_string(x=x_var, y=y_var)) + 
    geom_point() + 
    geom_smooth(method = "glm", formula = y ~ poly(x, 1), colour="black") + 
    labs(x = "Age", y="Parameter estimate") + 
    ggtitle(title) +
    theme_classic(base_size=14) + 
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.y=element_blank())
  return(p)
}

# Generate plots
invTemp_age <- generate_plot(PavBias_overall, "age", "invTemp", "Inverse temperature")
alpha_age <- generate_plot(PavBias_overall, "age", "alpha", "initial learning rate")
reward_age <- generate_plot(PavBias_overall, "age", "reward", "initial stimulus and action values")
w_age <- generate_plot(PavBias_overall, "age", "w2", "w2")

# Combine plots horizontally
param_est_fig <- plot_grid(invTemp_age, alpha_age, reward_age,w_age,
                           labels = c('a', 'b','c','d'), 
                           align="h", 
                           axis = "bt",
                           nrow=1)

# Plot the combined figure
plot(param_est_fig)

# Perform linear model analyses and correlations for each parameter
# - Models
# - ANOVA
# - Summary statistics
# - Correlation results
# Inverse Temperature
InvTemp_age.m <- lm(invTemp ~ z_age, data = param_df_age)
InvTemp_ageSq.m <- lm(invTemp ~ (z_age + z_ageSq), data = param_df_age)
anova(InvTemp_age.m, InvTemp_ageSq.m)
summary(InvTemp_age.m)
cor_results_invTemp <- get_cor_results(param_df_age, "invTemp", "z_age")
cor_results_invTemp
# Alpha (prior confidence)
alpha_age.m <- lm(alpha ~ z_age, data = param_df_age)
alpha_ageSq.m <- lm(alpha ~ (z_age + z_ageSq), data = param_df_age)
anova(alpha_age.m, alpha_ageSq.m)
summary(alpha_age.m)
cor_results_alpha <- get_cor_results(param_df_age, "alpha", "z_age")
cor_results_alpha
# Reward (prior reward)
reward_age.m <- lm(reward ~ z_age, data = param_df_age)
reward_ageSq.m <- lm(reward ~ (z_age + z_ageSq), data = param_df_age)
anova(reward_age.m, reward_ageSq.m)
summary(reward_age.m)
cor_results_reward <- get_cor_results(param_df_age, "reward", "z_age")
cor_results_reward
# W2
w2_age.m <- lm(w2 ~ z_age, data = param_df_age)
w2_ageSq.m <- lm(w2 ~ (z_age + z_ageSq), data = param_df_age)
anova(w2_age.m, w2_ageSq.m)
summary(w2_age.m)
cor_results_w2 <- get_cor_results(param_df_age, "w2", "z_age")
cor_results_w2
```
